Fractional anisotropy as an optimal tracer of cosmic voids

### 2014-07-29 cosmic_voids.tex
Abstract and another part of the introduction

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Fractional anisotropy as an optimal tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sbustama@pegasus.udea.edu.co}$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

\begin{abstract}

@@

\begin{keywords}
Cosmology: large-scale Structure of Universe, 
galaxies: star formation - line: formation
\end{keywords}

@@

Since voids where discovered in the first compiled galaxy surveys 
\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
Kirshner87}, they have been identified, along with the filamentary and 
hierarchically clustered nature of the cosmic web, as one of the most 
striking features of the Megaparsec universe \citep{Bond96}. Nevertheless,
due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
h^{-1}$), statistically significant catalogues of voids \citep{Pan10, 
Sutter12b, Nadathur14} only have become available after modern large 
galaxy surveys like the two-degree field Galaxy Survey \citep{Colless01,
Colless03} and the Sloan Digital Sky Survey \citep{York00,Abazajian03}, 
thereby triggering a plethora of more refined observational and 
statistical studies of voids throughout the last decade \citep{Hoyle04,
Croton04, Rojas05, Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b, 
Tikhonov07, BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}

On the theoretical side, early descriptions of the evolution of the 
large-scale universe, leaded by the seminal work of \citet{Zeldovich70}, 
are highly consistent with the cosmic web picture, where planar 
pancake-like regions of matter enclose enormous sub-dense voids and are 
bordered, in turn, by thin filaments and high-density clumpy knots. First
theoretical models for describing formation, dynamics and properties of
voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were quickly
complemented and extended by first numerical studies based on simulations
\citep{Martel90, Regos91, Weygaert93, Dubinski93}. This tendency of using
numerical results from N-body simulations, fuelled by last generation 
computing systems, has become increasingly common in the two last decades
as a powerful analysis tool in studies of cosmic voids \citep{Gottlober03}.

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Fractional anisotropy as an optimal tracer of cosmic voids}
\author[S. Bustamante and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Sebastian Bustamante \thanks{sbustamante@udea.edu.co}$^{1}$,
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^1$Instituto de F\'{\i}sica - FCEN, Universidad de Antioquia, Calle
67 No. 53-108, Medell\'{\i}n, Colombia\\ 
$^2$Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

\begin{abstract}
In the last decades voids have been identified as one of the most 
important features of the Megaparsec Universe, therefore a full 
understanding of their properties is required in order to a proper 
description of the large-scale structure of the Cosmic Web. Identifying
voids in cosmological observations and N-body simulations is hence an 
important enterprise that must be carried out and accordingly, a plethora 
of different void finding techniques can be found in the literature.

We present here a novel approximation for finding voids in cosmological 
simulations based upon two different schemes commonly used for quantifying
the cosmic web, i.e. the T-web and the V-web (the so-called web schemes), 
which have proven to be very adequate for that purpose. Unlike previously 
defined void finding techniques based on the density field, we use here 
the fractional anisotropy (FA) computed from the eigenvalues of each web 
scheme and then, through a Watershed Transform, we identify individual 
voids as the catching basins of local minima of the FA field. Like other 
Watershed Transform-based schemes, ours retains the same advantages, i.e., 
it is relatively free-parameter and makes no significant assumptions on 
the shape and structure of voids.

We test our method on the Bolshoi simulation and compare it with a
density-based scheme. We find our method gives a better resemblance to the
visual impression of the cosmic web in addition to a more robust 
description of voids as it allows to identify, in a very clear manner, 
their spatial limits as regions where the FA is maximized, normally 
corresponding to walls and filaments. This is mainly because of the 
non-monotonic behaviour of the FA, what allows to use it as a sort of 
one-dimensional tomography of the cosmic web.

@@

\begin{keywords}
Cosmology: theory - large-scale structure of Universe -
Methods: data analysis - numerical - N-body simulations
\end{keywords}

@@

Since voids where discovered in the first compiled galaxy surveys 
\citep{Chincarini75, Gregory78, Einasto80M, Einasto80N, Kirshner81, 
Kirshner87}, they have been identified, along with the filamentary and 
hierarchically clustered nature of the cosmic web, as one of the most 
striking features of the Megaparsec Universe \citep{Bond96}. Nevertheless,
due to the large volume extension of void regions ($\sim 5-10\ \mbox{Mpc} 
h^{-1}$), statistically significant catalogues of voids \citep{Pan10, 
Sutter12b, Nadathur14} only have become available after modern large 
galaxy surveys like the two-degree field Galaxy Survey \citep{Colless01,
Colless03} and the Sloan Digital Sky Survey \citep{York00,Abazajian03}, 
thereby triggering a plethora of more refined observational and 
statistical studies of voids throughout the last decade \citep{Hoyle04,
Croton04, Rojas05, Ceccarelli06, Patiri06a, Tikhonov06, Patiri06b, 
Tikhonov07, BendaBeckmann08, Foster09, Ceccarelli13, Sutter14a}

On the theoretical side, early descriptions of the evolution of the 
large-scale Universe, leaded by the seminal work of \citet{Zeldovich70}, 
are highly consistent with the cosmic web picture, where planar 
pancake-like regions of matter enclose enormous sub-dense voids and are 
bordered, in turn, by thin filaments and high-density clumpy knots. First
theoretical models for describing formation, dynamics and properties of
voids \citep{Hoffman82, Icke84, Bertschinger85, Blumenthal92} were quickly
complemented and extended by first numerical studies based on simulations
\citep{Martel90, Regos91, Weygaert93, Dubinski93}. This tendency of using
numerical data from N-body simulations, fuelled by last generation 
computing systems, has become increasingly common in the last years as a 
powerful analysis toolkit of cosmic voids (for an extensive compilation of 
previous numerical works, see \citet{Colberg08}).
